Market-based Mechanisms for Resource Scheduling

### 2013-12-18 paper/paper.tex
Better image placement
More changes.

Large-scale computing clusters offer the potential for greater efficiency through
pooling of computational resources, but must contend with the problem of
allocating these resources to users with competitive and potentially
incompatible demands. Such conflicts are typically arbitrated by some \emph{fairness}
criterion, such as dominant resource fairness (DRF) \cite{drf}, which benefit from their
simplicity, efficiency, and non-manipulability. Unfortunately, when applied in
realistic settings --- when dealing with inhomogeneous resources, time-varying
demands or deadlines, requirements for data locality, etc.---typical implementations
of these systems cease to be either
efficient or non-manipulable.

@@

\subsection{Microeconomic methods}
In this paper we confront the challenge of modifying Mesos to provide more
robust efficiency guarantees, without compromising its agnosticism regarding the
nature of different frameworks' desiderata. We propose \emph{price signals} as a
mechanism for accomplishing this; instead of accepting or rejecting a resource
offer, a framework can express its preferences by assigning a \emph{willingness
to pay} for that resource, and Mesos can give the resources to whichever
frameworks are most willing to pay.

We stress the distinction between this use of price signals and the more typical
motivation. We are most interested in price signals as an \emph{abstraction} which
programs can use to express their constraints, rather than as a mechanism to
extract revenue for the cluster operator or to arbitrate between competing
external interests. To consider a simple case, suppose there are two programs
that are contending for a shared resource $R$. Each could either make use of $R$ or
some alternative resource $R'$ (for example, a different machine in the cluster at
a different time). Our proposal is to have each program articulate the value of
resource $R$ (compared to the benchmark of not receiving resource $R$, and then
contending for resource $R'$ at a later date). The primary alternatives that have
been considered are:
\vspace{-4mm}
\begin{enumerate}
\itemsep0em
  \item Ignore the relative value of resource $R$ and $R'$, and make allocation
    decisions entirely on the basis of fairness considerations (for example by
    ensuring that each framework has an equal number of every resource). This is
    the approach taken by Mesos, although it in fact achieves better behavior
    precisely by \emph{violating} the strategy-proofness of its underlying allocation
    policy, and providing incentives to frameworks to strategically decline a
    resource in order to receive a better allocation in the future.
  \item Understand the entire optimization problem faced by each problem, and
    make explicit judgements of the relative value of $R$ and $R'$ within the
    scheduler. This violates the spirit of Mesos, and in general appears to be
    difficult given the complexity and scale of the cluster scheduling problem.
\end{enumerate}

@@

\begin{table}[t!]
%\begin{center}
    \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    Desired & \small DRF & \small DRF & \small Market-based  \\
    Properties & \small(simple) & \small (realistic) & \small Mechanism \\
    \hline
    \small Envy-Free & \cmark &  & Locally \\
    \small Pareto-Efficient & \cmark & Locally & Locally  \\
    \small Strategy-proof & \cmark & Locally  & Locally \\
    \small Sharing incentive & \cmark &  & \cmark\\
    \hline
    \end{tabular}
%\end{center}
  \caption{Properties of DRF in a simple environment
 compared with properties of DRF and our economic mechanism
 in a more realistic environment (see section~\ref{drawbacks}).}
  \label{table:props}
\end{table}

@@

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{images/util_high.png}
\caption{Utilization achieved by DRF and our policy on a simulated 25-node CPU-bound cluster.  DRF's average utilization is 98\% average utilization while ours is 99\%.}
\label{img:util_high}
\end{figure}

@@

This paper presented an initial investigation into the possibility of leveraging prices and a market-based mechanism for resource scheduling. We describe a protocol for use in the Mesos cluster scheduler with beneficial theoretical properties. Simulation evaluation shows that our market-based mechanism can perform reasonably in a backwards-compatible mode, where no economic information is provided. When economic data exists, our approach can provide substantial performance benefits.

>>>>

Large-scale computing clusters offer the potential for greater efficiency through
pooling of computational resources, but must contend with the problem of
allocating these resources to users with competitive and potentially
incompatible demands. Such conflicts are typically arbitrated by some \emph{fairness}
criterion, such as dominant resource fairness (DRF) \cite{drf}, which benefit from their
simplicity, efficiency, and non manipulability. Unfortunately, when applied in
realistic settings --- when dealing with inhomogeneous resources, time-varying
demands or deadlines, requirements for data locality, etc.---typical implementations
of these systems cease to be either
efficient or non-manipulable.

@@

In this paper we confront the challenge of modifying Mesos to provide more
robust efficiency guarantees, without compromising its agnosticism regarding the
nature of different frameworks' desiderata. We propose \emph{price signals} as a
mechanism for accomplishing this; instead of accepting or rejecting a resource
offer, a framework can express its preferences by assigning a \emph{willingness
to pay} for that resource, and Mesos can give the resources to whichever
frameworks are most willing to pay.

@@

\begin{table}[t!]
%\begin{center}
    \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    Desired & \small DRF & \small DRF & \small Market-based  \\
    Properties & \small(simple) & \small (realistic) & \small Mechanism \\
    \hline
    \small Envy-Free & \cmark &  & Locally\footnote{No framework envies a framework that pays less.} \\
    \small Pareto-Efficient & \cmark & Locally\footnote{With caveats arising from computational hardness of packing problems.} & Locally\footnote{With caveats arising from computational hardness of packing problems}  \\
    \small Strategy-proof & \cmark & Locally  & Locally \\
    \small Sharing incentive & \cmark &  & \cmark\\
    \hline
    \end{tabular}
%\end{center}
  \caption{Properties of DRF in a simple environment
 compared with properties of DRF and our economic mechanism
 in a more realistic environment (see section~\ref{drawbacks}).}
  \label{table:props}
\end{table}

@@

\begin{figure}[ht]
\includegraphics[width=0.5\textwidth]{images/util_high.png}
\caption{Utilization achieved by DRF and our policy on a simulated 25-node CPU-bound cluster.  DRF's average utilization is 98\% average utilization while ours is 99\%.}
\label{img:util_high}
\end{figure}

@@

@@

This paper presented an initial investigation into the possibility of leveraging prices and a market-based mechanism for resource scheduling. We describe a protocol for use in the Mesos cluster scheduler with beneficial theoretical properties. Simulation evaluation shows that our market-based mechanism can perform reasonably in a backwards-compatible mode, where no economic information is provided. 
We also provide theoretical and experimental evidence that our approach can help manage difficulties
resulting from constraints that are unknown to the scheduler.
